Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-04 snTomas.tex
Various changes, incorporating comments from various co-authors

\begin{abstract}
SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
$z=1.31\pm0.01$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
SN has a projected separation from the cluster core of
$\sim$40\arcsec, closer to the critical lensing line than any previous
cluster-lensed \SNIa.  As such, it provides the first opportunity to
confront gravitational lens models of galaxy clusters with the direct
measurement of an absolute magnification at the edge of the
strong-lensing region.  We derive a tightly constrained measure of the
peak apparent magnitude, corrected for light curve shape and
exinction.  In a cosmology-independent analysis, we find that \tomas\
is \change{$0.75\pm0.15$} magnitudes brighter than unlensed \SNeIa\ at
similar redshift, implying a lensing magnification
of \change{$\mu_{\rm obs}=2.00\pm0.28$}.  We compare this direct
measurement of the magnification against predicted magnifications
from \change{14 lens models,} representing a broad range of
methodologies and incorporating a variety of strong- and weak-lensing
constraints.  The models are collectively fairly accurate. \change{
Half of the models deliver median magnifications that are consistent
with the measured $\mu$ to within the 1$\sigma$ uncertainties.}
However, the models are systematically biased to higher values: none
of the tested models predict a magnification equal to or lower than
the observed $\mu$, and some models are more than $5\sigma$ above the
measured magnification.  We evaluate possible causes for this bias,
and find that intercomparison of the lens models rules out several
simple possibilities.  A larger sample of $\sim$10 \SNeIa\ behind any
single cluster could provide a robust evaluation of systematic biases
in lens models.  Until such a sample exists, it is advisable
to \change{increase the estimated uncertainty of predicted
magnifications to match the dispersion observed across multiple lens
models.}
\end{abstract}

@@

\change{
One of the key values in observing standard candles behind
gravitational lenses is that {\it all} lensing reconstructions suffer
from the mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
degeneracy arises because one can introduce into a lens model an
unassociated sheet of mass in front of or behind the lens, without
disturbing the primary observable quantities.  For example, take a
lens model with a given surface mass density $\kappa$, and then
transform the surface mass density to
$\kappa^{\prime}=(1-\lambda)\kappa+\lambda$ for any arbitrary value
$\lambda$.  Both the $\kappa$ and $\kappa^{\prime}$ models will
produce exactly the same values for all positional and shear
constraints from strong and weak lensing.  This is the simplest case
illustrating a positional constraint degeneracy, but there are more
complex versions \citep{Schneider:2014}.  Such mass sheet
degeneracies do not extend to the {\it absolute} magnification of a
background source's flux and size.  Therefore, an absolute measurement
of magnification from a standard candle or a standard ruler
\citep{Sonnenfeld:2011}  can break this fundamental degeneracy
\citep{Holz:2001}.
}

@@

Finally, we repeat the fitting, but without any warping of the
templates to account for differences in the continuum shape.  In this
iteration we only allow each template SED to be scaled in flux
coherently at all wavelengths.  As shown in Figure~\ref{fig:SpecFit},
we again find that the \tomas\ SED can be matched by a normal Type Ia
SN (SN 2011fe) at redshift $z=1.31\pm0.01$.  Without the continuum
warping, an alternative fit also arises: the normal Type Ia SN 2011iv
at $z=0.98\pm0.01$. Formally, this match provides a slightly better
fit to the unwarped \tomas\ spectrum, although the fit is notably poor
at $\sim8700$\AA\ where the most significant absorption feature is
found. Furthermore, a redshift $z\sim1$ is at odds with the host
galaxy photo-z ($1.5\pm0.2$), and we will see in the following section
that the photometric data is incompatible with a normal Type Ia SN at
$z\sim1.0$.

@@

\change{
Recent work has highlighted the inadequacy of this simplistic approach
for handling intrinsic scatter in the Type Ia SN
population \citep{Marriner:2011,Kessler:2013,Mosher:2014,Scolnic:2014a,Betoule:2014},
but a full consideration of those alternative approaches is beyond the
scope of this work.  We adopt the simple approach of using a single
empirically defined value for $\sigma_{\rm int}$, reflecting
principally an intrinsic scatter in Type Ia SN intrinsic luminosity
that is fixed across time and phase.  Measurements of $\sigma_{\rm
int}$ range from 0.08 mag \citep{Jha:2007,Conley:2011} to 0.15
mag \citep{Kessler:2009b,Suzuki:2012}.  We adopt a value of
$\sigma_{\rm int}=0.08$ mag, as derived by \citet{Jha:2007}
and \citet{Conley:2011}.  Although this is on the low end of the range
reported in the literature, this value is the most appropriate to
apply to our analysis for two reasons.  First and foremost, for the
SALT2 fitter we are using light curve fit parameters
($\alpha$,$\beta$) with associated uncertainties that have been
derived from the joint analysis of \citet{Conley:2011}
and \citet{Sullivan:2011}. Similarly, the implementation of MLCS2k2
that we have used is based on the uncertainty model derived from model
training in \citet{Jha:2007}.  Inflating $\sigma_{int}$ beyond 0.08
mag would therefore be equivalent to driving the reduced $\chi^2$ of
the Type Ia SN Hubble diagram to $<1$.  Second, the value of 0.08 mag
determined in \citet{Conley:2011} is specific to the HST SN sample,
from \citet{Riess:2007} and \citet{Suzuki:2011}, which is the SN
subset that is most similar to \tomas\ in terms of redshift and data
analysis.  Larger values for $\sigma_{\rm int}$ are typically
associated with SN samples at significantly lower redshifts that have
less homogeneous data collection and analysis. }

@@

\change{
The physical mechanism that drives the mass step is not yet
understood, but may be related to the metallicity or age of the SN
progenitor systems. In either case, it is reasonable to expect that
the significance of this effect decreases with redshift, as metal-rich
passive galaxies become much less common at $z>1$.  Indeed, when the
size of the mass step correction is allowed to vary with redshift,
there is no significant evidence that a non-zero mass step is required
at $z>1$ \citep{Rigault:2013,Shafer:2014,Betoule:2014}.  Given the
absence of a clear physical model and the lack of empirical support
for a high-$z$ mass step, we do not apply any correction to SN \tomas
or the control sample.
}

@@

The unlensed sample comprises 18 spectroscopically confirmed Type Ia
SNe in the range $1.14\leq z \leq1.42$ from the GOODS and SCP
surveys,\footnote{GOODS: Great Observatories Origins Deep Survey,
PI:Giavalisco, HST-PID:9425,9583; SCP: Supernova Cosmology Project,
PI:Perlmutter} which used the HST Advanced Camera for
Surveys \citep{Riess:2006,Suzuki:2012}.  Using the SALT2 and MLCS2k2
fitters as described above, we get distance modulus measures for every
object in this control sample.  We then fit a linear relationship for
distance modulus vs. redshift, and derive a prediction for the
distance modulus of a normal Type Ia SN at the redshift of SN \tomas
(Figure~\ref{fig:MagnificationMeasurement}).
This predicted value is given in
Table~\ref{tab:MeasuredMagnification} under the ``Control'' column.
The difference between the observed distance of SN \tomas\ and this
control sample value is attributed to the magnification from
gravitational lensing:

@@

@@

However, beyond this first-order agreement, there is a systematic bias
apparent. All of the lens models predict a magnification that is {\it
higher} than the observed value, and no model has a median value that
falls within the $1\sigma$ range of the observed magnifications.  It
is important to emphasize that SN \tomas\ only samples a single
sight-line through the cluster, so any conclusions to be drawn from
this analysis are necesssarily limited.  Nevertheless, a systematic shift
common to all models is surprising, given the wide range of modeling
strategies, input data, and physical assumptions represented by this
set of models.  In the following subsections we examine possible
explanations for this apparently universal bias.

@@

\change{
Resolving the identification of this single multiply-imaged galaxy
could be an important component in resolving the magnification
discrepancy, though it is unlikely to completely remove the tension.
It is true that the model that reassigns the position to \33p\
({\tt Jauzac}) is also the one with the largest deviation from our
observed $\mu$ value.  However, the bias is still present even if we
remove that model and only consider models using the original position
3.3.  
}

\subsection{Mass Profile Truncation}
\label{sec:MassProfileTruncation}

Eight of the mass models evaluated here are constrained only using
strong-lensing features such as multiply-imaged background galaxies
and highly magnified arcs.  There are now $\sim$150 known lensed
images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
located several arcseconds outside the core region of the cluster
where these multiply-imaged galaxies are found.  Therefore these seven
``strong-lensing only'' models must necessarily rely on extrapolations
to provide a prediction for the SN \tomas\ magnification.  If the true
cluster density profile for Abell 2744 happens to be truncated -- with
a sharp drop right at the edge of this core strong-lensing region --
then these seven models might well overestimate the mass interior to
the \tomas\ position, and thus systematically overestimate the
magnification.

The other three models in our comparison set also use the strong
lensing constraints from the core region, but additionally utilize weak
lensing measurements to provide additional constraints on the mass
distribution farther from the cluster core.  The signal from weak
lensing relies on a large sample of background galaxies, so this
constraint operates principally at separations more than 1\arcmin from
the cluster core.  At a projected separation of $\sim40\arcsec$,
SN \tomas\ falls in between the strong- and weak-lensing regimes, and
one would expect that models incorporating both of those constraints
would be less susceptible to the systematic bias of a truncated mass
profile.  The lowest magnification estimate in our sample (from the
Merten model) is among this sub-sample.  However, we find that
collectively these three strong+weak models (shown as diamonds in
Figure~\ref{fig:lensingtest}) exhibit the same propensity to
overestimate the magnification along this line of sight.  Thus, a
sudden change in the mass profile outside the strong lensing region is
not a likely explanation for this small systematic bias.

With two versions of the CATS model, we also have a more direct test
of the effect of introducing weak lensing constraints.  The initial
CATS model uses only strong-lensing constraints, and gives
$\mu=2.27^{+0.05}_{-0.04}$, slightly higher than the measured value.
A second iteration of this model, labeled here as CATS-SL+WL, used the
same strong-lensing features, but added in weak lensing constraints.
The revised magnification of $\mu=2.62\pm0.18$ is further from the
measured value, which serves to reinforce the conclusion that adding
weak lensing constraints cannot resolve this bias.

@@

\change{
We have adopted the spectroscopic redshift of $z=1.31\pm0.01$ for the
magnification comparison.  Spectroscopic redshifts are generally more
precise and accurate than those derived from photometric
observations \citep{Rodney:2010b,Kessler:2010,Sako:2011}.  However, in
this case the spectrum is limited to the rest-frame near-UV
wavelengths, where the available SN spectral template libraries are
more limited than at optical wavelengths.  If we use the photometric
redshift of $z=1.35\pm0.02$ instead, then the measured magnification
is reduced.\footnote{By increasing the redshift, the SN is presumed to
be at a greater distance, so to first order one would be expect it to
appear slightly fainter (larger distance modulus). If the distance
modulus inferred from the light curve fit remained constant, this
would drive the inferred magnification to a higher value.  However,
the light curve fitting is more strongly affected by the covariance
between redshift, color, and light curve width.  In this case, these
effects drive the distance modulus to a larger value at $z=1.35$,
resulting in a smaller value of the observed magnification $\mu$.}
From the SALT2 fitter we derive $\mu_{\rm SALT2}=1.80\pm0.30$ and from
MLCS2k2 we get $\mu_{\rm MLCS2k2}=1.83\pm0.17$.  The lens models are
also shifted, and they uniformly move in the opposite direction, to
magnification values that are {\it larger} than at $z=1.31$, by
$\sim1$\%.  Thus, shifting the SN to the photometric redshift of
$z=1.35$ only serves to (slightly) exacerbate the tension between the
observations and models.
}

@@

\change{
In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
the blue end of the normal range of Type Ia SN colors.  With the SALT2
fitter we measured a color parameter $c=-0.115\pm0.025$, and with
MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
V}=0.014\pm0.037$ magnitudes.  These colors are tightly constrained,
as we are fitting to photometry that covers a rest-frame wavelength
range from $\sim3500-7000$\AA and extends to $\sim$30 days past
maximum brightness.  This leaves little room for the luminosity
measurement to be biased by dust, as the dimming of \tomas\ would also
necessarily be accompanied by some degree of reddening. 
}

@@

This work is dedicated to our colleague and friend Tomas Dahlen
(-2014), for whom this supernova has been named in memorium. He is
greatly missed.

@@

>>>>

\begin{abstract}
SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
$z=1.31\pm0.01$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
SN has a projected separation from the cluster core of
$\sim$40\arcsec, closer to the critical lensing line than any previous
cluster-lensed \SNIa.  As such, it provides a valuable opportunity to
confront gravitational lens models of galaxy clusters with the direct
measurement of an absolute magnification at the edge of the
strong-lensing region.  We derive a tightly constrained measure of the
peak apparent magnitude, corrected for light curve shape and
exinction.  In a cosmology-independent analysis, we find that \tomas\
is \change{$0.75\pm0.15$} magnitudes brighter than unlensed \SNeIa\ at
similar redshift, implying a lensing magnification
of \change{$\mu_{\rm obs}=2.00\pm0.28$}.  We compare this direct
measurement of the magnification against predicted magnifications
from \change{14 lens models,} representing a broad range of
methodologies and incorporating a variety of strong- and weak-lensing
constraints.  The models are collectively fairly accurate. \change{
Half of the models deliver median magnifications that are consistent
with the measured $\mu$ to within the 1$\sigma$ uncertainties.}
However, the models are systematically biased to higher values: none
of the tested models predict a magnification equal to or lower than
the observed $\mu$, and some models are more than $5\sigma$ above the
measured magnification.  We evaluate possible causes for this bias,
and find that intercomparison of the lens models rules out several
simple possibilities.  A larger sample of $\sim$10 \SNeIa\ behind any
single cluster could provide a robust evaluation of systematic biases
in lens models.  Until such a sample exists, it is advisable
to \change{increase the estimated uncertainty of predicted
magnifications to match the dispersion observed across multiple lens
models.}
\end{abstract}

@@

\change{
One of the key values in observing standard candles behind
gravitational lenses is that most lensing reconstructions suffer from
the mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
degeneracy arises because one can introduce into a lens model an
unassociated sheet of mass in front of or behind the lens, without
disturbing the primary observable quantities.  For example, take a
lens model with a given surface mass density $\kappa$, and then
transform the surface mass density to
$\kappa^{\prime}=(1-\lambda)\kappa+\lambda$ for any arbitrary value
$\lambda$.  Both the $\kappa$ and $\kappa^{\prime}$ models will
produce exactly the same values for all positional and shear
constraints from strong and weak lensing.  When lensed background
sources are available across a wide range of redshifts (as is the case
for the Abell 2744 cluster discussed here), it should in principle be
possible to account for the simplest form of a single mass sheet
within that redshift range.  However, there are more complex versions
of positional constraint
degeneracies \citep{Schneider:2014,Liesenborgs:2012}.  Such
degeneracies do not extend to the {\it absolute} magnification of a
background source's flux and size.  Therefore, an absolute measurement
of magnification from a standard candle or a standard ruler
\citep{Sonnenfeld:2011}  can break these fundamental degeneracies
\citep{Holz:2001}.
}

@@

Finally, we repeat the fitting, but without any warping of the
templates to account for differences in the continuum shape.  In this
iteration we only allow each template SED to be scaled in flux
coherently at all wavelengths.  As shown in Figure~\ref{fig:SpecFit},
we again find that the \tomas\ SED can be matched by a normal Type Ia
SN (SN 2011fe) at redshift $z=1.31\pm0.01$.  Without the continuum
warping, an alternative fit also arises: the \change{fast-declining
(91bg-like)} Type Ia SN 2011iv
at $z=0.98\pm0.01$. Formally, this match provides a slightly better
fit to the unwarped \tomas\ spectrum, although the fit is notably poor
at $\sim8700$\AA\ where the most significant absorption feature is
found. Furthermore, a redshift $z\sim1$ is at odds with the host
galaxy photo-z ($1.5\pm0.2$), and we will see in the following section
that the photometric data is also incompatible with a Type Ia SN at
$z\sim1.0$.

@@

\change{
Recent work has highlighted the inadequacy of this simplistic approach
for handling intrinsic scatter in the Type Ia SN
population \citep{Marriner:2011,Kessler:2013,Mosher:2014,Scolnic:2014a,Betoule:2014},
but a full consideration of those alternative approaches is beyond the
scope of this work.  We adopt the simple approach of using a single
empirically defined value for $\sigma_{\rm int}$, reflecting
principally an intrinsic scatter in Type Ia SN intrinsic luminosity
that is fixed across time and phase.  Measurements of $\sigma_{\rm
int}$ range from 0.08 mag \citep{Jha:2007,Conley:2011} to 0.15
mag \citep{Kessler:2009b,Suzuki:2012}.  We adopt a value of
$\sigma_{\rm int}=0.08$ mag, as derived by \citet{Jha:2007}
and \citet{Conley:2011}.  Although this is on the low end of the range
reported in the literature, this value is the most appropriate to
apply to our analysis for two reasons.  First and foremost, for the
SALT2 fitter we are using light curve fit parameters
($\alpha$,$\beta$) with associated uncertainties that have been
derived from the joint analysis of \citet{Conley:2011}
and \citet{Sullivan:2011}. Similarly, the implementation of MLCS2k2
that we have used is based on the uncertainty model derived from model
training in \citet{Jha:2007}.  Inflating $\sigma_{int}$ beyond 0.08
mag would therefore be equivalent to driving the reduced $\chi^2$ of
the Type Ia SN Hubble diagram to $<1$.  Second, the value of 0.08 mag
determined in \citet{Conley:2011} is specific to the HST SN sample,
from \citet{Riess:2007} and \citet{Suzuki:2012}, which is the SN
subset that is most similar to \tomas\ in terms of redshift and data
analysis.  Larger values for $\sigma_{\rm int}$ are typically
associated with SN samples at significantly lower redshifts that have
less homogeneous data collection and analysis. }

@@

\change{
The physical mechanism that drives the mass step is not yet
understood, but may be related to the metallicity or age of the SN
progenitor systems. In either case, it is reasonable to expect that
the significance of this effect decreases with redshift, as metal-rich
passive galaxies become much less common at $z>1$.  Indeed, when the
size of the mass step correction is allowed to vary with redshift,
there is no significant evidence that a non-zero mass step is required
at $z>1$ \citep{Rigault:2013,Shafer:2014,Betoule:2014}.  Given the
absence of a clear physical model and the lack of empirical support
for a high-$z$ mass step, we do not apply any correction to SN \tomas\ 
or the control sample.  }

@@

The unlensed sample comprises 18 spectroscopically confirmed Type Ia
SNe in the range $1.14\leq z \leq1.42$ from the GOODS and SCP
surveys,\footnote{GOODS: Great Observatories Origins Deep Survey,
PI:Giavalisco, HST-PID:9425,9583; SCP: Supernova Cosmology Project,
PI:Perlmutter} which used the HST Advanced Camera for
Surveys \citep{Riess:2006,Suzuki:2012}.  Using the SALT2 and MLCS2k2
fitters as described above, we get distance modulus measures for every
object in this control sample.  We then fit a linear relationship for
distance modulus vs. redshift, and derive a prediction for the
distance modulus of a normal Type Ia SN at the redshift of SN \tomas\
(Figure~\ref{fig:MagnificationMeasurement}).
This predicted value is given in
Table~\ref{tab:MeasuredMagnification} under the ``Control'' column.
The difference between the observed distance of SN \tomas\ and this
control sample value is attributed to the magnification from
gravitational lensing:

@@

\change{
In general, free-form methods tend to explore the model parameter
space more fully than parametric methods. This is reflected in the
size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
GRALE, which has the largest, and possibly the most realistic
uncertainties is able to account for mass sheet degeneracy by
introducing a free parameter in the reconstruction that represents an
arbitrarily positioned mass sheet, with normalization to be chosen by
the genetic algorithm.  More complex degeneracies are also accounted
for in GRALE through the use of basis
functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}
}

@@

However, beyond this first-order agreement, there is a systematic bias
apparent. All of the lens models \change{return median magnifications
that are} {\it higher} than the observed value, and \change{half of
the models are discrepant by more than $1\sigma$.}  It is important to
emphasize that SN \tomas\ only samples a single sight-line through the
cluster, so any conclusions to be drawn from this analysis are
necesssarily limited.  Nevertheless, a systematic shift common to all
models is surprising, given the wide range of modeling strategies,
input data, and physical assumptions represented by this set of
models.  In the following subsections we examine possible explanations
for this \change{small but} apparently universal bias.

@@

\change{
Resolving the identification of this single multiply-imaged galaxy
could be a component in resolving the magnification
discrepancy, though it is unlikely to completely remove the tension.
It is true that the model that reassigns the position to \33p\
({\tt Jauzac}) is also the one with the largest deviation from our
observed $\mu$ value.  However, \citet{Jauzac:2014c} have already
evaluated the impact of relocating this single source, and
they find that it is not responsible for the observed increase in
magnifications across the field. Rather, the 
primary cause for the general magnification increase is the addition
of new multiple images in the Northern region, detected using the new
HFF data. }

\subsection{Mass Profile Extrapolation}
\label{sec:MassProfileExtrapolation}

Eight of the mass models evaluated here are constrained only using
strong-lensing features such as multiply-imaged background galaxies
and highly magnified arcs.  There are now $\sim$150 known lensed
images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
located several arcseconds outside the core region of the cluster
where these multiply-imaged galaxies are found.  Therefore these eight
``strong-lensing only'' models must necessarily rely on extrapolations
to provide a prediction for the SN \tomas\ magnification.  Let us
suppose that the true cluster density profile for Abell 2744 happens
to have a sharp drop right at the edge of this core strong-lensing
region. In that case these eight models might well overestimate the
mass interior to the \tomas\ position, and thus systematically
overestimate the magnification.

The other three models in our comparison set also use the strong
lensing constraints from the core region, but additionally utilize
weak lensing measurements to provide additional constraints on the
mass distribution farther from the cluster core.  The signal from weak
lensing relies on a large sample of background galaxies, so this
constraint operates principally at separations more than 1\arcmin\ from
the cluster core.  At a projected separation of $\sim40\arcsec$,
SN \tomas\ falls in between the strong- and weak-lensing regimes, and
one would expect that models incorporating both of those constraints
would be less susceptible to the systematic bias of a sharply
steepening mass profile.  The lowest magnification estimate in our
sample (from the Merten model) is among this sub-sample.  However, we
find that collectively these three strong+weak models (shown as
diamonds in Figure~\ref{fig:lensingtest}) exhibit the same propensity
to overestimate the magnification along this line of sight.  Thus, a
sudden change in the mass profile outside the strong lensing region is
not a likely explanation for this small systematic bias.

With two versions of the CATS model, we also have a more direct test
of the effect of introducing weak lensing constraints.  The initial
CATS model uses only strong-lensing constraints, and gives
$\mu=2.27^{+0.05}_{-0.04}$, slightly higher than the measured value.
A second iteration of this model, labeled here as CATS-SL+WL, used the
same strong-lensing features, but added in weak lensing constraints.
The revised magnification of $\mu=2.62\pm0.18$ is further from the
measured value, which serves to reinforce the conclusion that adding
weak lensing constraints cannot, by itself, resolve this bias.

@@

\change{
We have adopted the spectroscopic redshift of $z=1.31\pm0.01$ for the
magnification comparison.  Spectroscopic SN redshifts are generally more
precise and accurate than those derived from SN
photometry \citep{Rodney:2010b,Kessler:2010,Sako:2011}.  However, in
this case the spectrum is limited to the rest-frame near-UV
wavelengths, where the available SN spectral template libraries are
more limited than at optical wavelengths.  If we use the photometric
redshift of $z=1.35\pm0.02$ instead, then the measured magnification
is reduced.\footnote{By increasing the redshift, the SN is presumed to
be at a greater distance, so to first order one would be expect it to
appear slightly fainter (larger distance modulus). If the distance
modulus inferred from the light curve fit remained constant, this
would drive the inferred magnification to a higher value.  However,
the light curve fitting is more strongly affected by the covariance
between redshift, color, and light curve width.  In this case, these
effects drive the distance modulus to a larger value at $z=1.35$,
resulting in a smaller value of the observed magnification $\mu$.}
From the SALT2 fitter we derive $\mu_{\rm SALT2}=1.80\pm0.30$ and from
MLCS2k2 we get $\mu_{\rm MLCS2k2}=1.83\pm0.17$.  The lens models are
also shifted, and they uniformly move in the opposite direction, to
magnification values that are {\it larger} than at $z=1.31$, by
$\sim1$\%.  Thus, shifting the SN to the photometric redshift of
$z=1.35$ only serves to (slightly) exacerbate the tension between the
observations and models.  }

@@

\change{
In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
the blue end of the normal range of Type Ia SN colors.  With the SALT2
fitter we measured a color parameter $c=-0.115\pm0.025$, and with
MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
V}=0.014\pm0.037$ magnitudes.  These colors are tightly constrained,
as we are fitting to photometry that covers a rest-frame wavelength
range from $\sim3500-7000$\AA\ and extends to $\sim$30 days past
maximum brightness.  This leaves little room for the luminosity
measurement to be biased by dust, as the dimming of \tomas\ would also
necessarily be accompanied by some degree of reddening. 
}

@@

This work is dedicated to our colleague and friend Tomas Dahlen, for
whom this supernova has been named in memorium. He is dearly missed.

@@

AM acknowledge the financial support of the Brazilian funding agency
FAPESP (Post-doc fellowship - process number 2014/11806-9)
